\chapter{Scientific Background}
%labels will help you to reference to certain images, tables, chapters, section, and so on...
\label{background}

DELETEME: This chapter will cover all of your background information and related work. Background and related work are directly related to your thesis. Please do not place irrelevant content here which is a common mistake. Citing will be handled in the appendices.

DELETEME: Background represents underlying knowledge that is required to understand your work. The expected knowledge level of your readers can be set to the one of a bachelor or master student who just finished his studies (depending on what kind of thesis you are writing). This means that you do not need to describe how computers work, unless your thesis topic is about this. Everything that an average alumnus from your field of studies should know does not need to be described. It turns, background information that is very complex and content-wise very near to your problem, can be placed in the main parts. Everything else should be written here. Note: it is important to connect each presented topic to your thesis. E.g. if you present the ISO/OSI layer model you should also write that this is needed to understand the protocols you plan to develop in the main parts.

DELETEME: Related work represents results from work that handled the same or a similar problem that you are addressing. This work might have used a different approach or might not have been that successful. Finding a paper / work that solved your problem in the same way you were planning to do is not good and you should contact your supervisor for solving this issue. Again, each paper / work has to be connected to your approach: other papers might have not chosen an optimal solution; they might not have been taking care of essential aspects; they might have chosen a different approach and you believe, yours will work better ...

%###################################################################################
%###################### Topic A             ########################################
%###################################################################################
\section{Topic 1}

%###################################################################################
%###################### Topic B             ########################################
%###################################################################################
\section{Topic 2}

%###################################################################################
%###################### Topic C             ########################################
%###################################################################################
\section{Topic 3}